---
title: Epiconcept qmd template
format:
  epidemioslides-revealjs: default
author: Yohann Mansiaux
date: last-modified
---

# Transition slide: use a level 1 title

## "Standard" slide: use a level 2 title

Hello World.

If you wish to know more about slides with Quarto, please visit <https://quarto.org/docs/presentations/revealjs/>

## Content

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.

# Use code

## Code

```{r}
#| echo: true
print("hello world")
```

## **Code with annotation**

```{r eval=FALSE, echo=TRUE}
library(tidyverse)
library(palmerpenguins)
penguins |> # <1>
  mutate( # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm # <2>
  ) # <2>
```

1. Take `penguins`, and then,
2. add new columns for the bill ratio and bill area.


## **Highlighted code**


::: {.columns}
::: {.column width="50%"}

```{.r code-line-numbers='1,2,4,7'}
library(tidyverse)
library(palmerpenguins)
penguins |>
  mutate(
    bill_ratio = bill_depth_mm / bill_length_mm,
    bill_area  = bill_depth_mm * bill_length_mm
  )
```
:::

::::

## **Highlighted code (progressively)**

::: {.columns}
::: {.column width="50%"}

```{.r code-line-numbers="1|2|4,7"}
library(tidyverse)
library(palmerpenguins)
penguins |>
  mutate(
    bill_ratio = bill_depth_mm / bill_length_mm,
    bill_area  = bill_depth_mm * bill_length_mm
  )
```

:::

::::


## **Use columns**

::: {.columns}
::: {.column width="30%"}

```{r eval = FALSE, echo=TRUE}
library(tidyverse)
library(palmerpenguins)
```

:::
::: {.column width="70%"}

```{r eval = FALSE, echo=TRUE}
penguins |>
  mutate(
    bill_ratio = bill_depth_mm / bill_length_mm,
    bill_area  = bill_depth_mm * bill_length_mm
  )
```
:::
::::


## 3 columns

::: {.columns}
::: {.column  width="33%"}

```{r eval = FALSE, echo=TRUE}
library(shiny)
library(dplyr)
library(ggplot2)
library(readr)

ui <- fluidPage(
  ...
)
```

:::
::: {.column width="33%"}


```{r eval = FALSE, echo=TRUE}
server <-
 function(input,
          output,
          session) {
  ...
}
```
:::
::: {.column width="33%"}


```{r eval = FALSE, echo=TRUE}
shiny::runApp()
```
:::
::::

## Align text

:::: {.columns}
::: {.column width="33%"}
By default text is left aligned.
:::

::: {.column .center-items width="33%"}
It can be centered by using the `center-items` class.
:::

::: {.column .right-items width="33%"}
It can also be right-align by using the `right-items` class.
:::
::::

# Lists

## List by default

- Eat spaghetti
- Drink wine

## Incremental list

By default number and bullet lists within slides are displayed all at once.

You can also explicitly make any list incremental or non-incremental by surrounding it in a div with an explicit class that determines the mode. 

::: {.incremental}
- Eat spaghetti
- Drink wine
:::


# Tabs

## Tabs demo

::: {.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::

# Components


## Call-outs

5 call outs can be used: 

`note`, `tip`, `warning`, `caution`, and `important`.

:::{.callout-warning}
Warning
:::

:::{.callout-note}
Note
:::

:::{.callout-tip}
Tip
:::

:::{.callout-caution}
Caution
:::

:::{.callout-important}
Important
:::